Data Specialization for a Staged Lambda Calculus

### 2015-02-16 paper/splitting.tex
various edits to splitting section

Similar to above, we also define a $\sepredtwosym$ relation which can be used to evaluate \texttt{sepM} terms,
with one complication arising from the fact that \lang\ terms at world \bbonem\ produces multistage output.
For example, consider the term
\begin{lstlisting}
(next {1+2}, pure{3+4})
\end{lstlisting}
which reduces (via $\redonesym$) to the residual table and partial value
\begin{lstlisting}
[yhat |-> 1+2] (next {yhat}, pure{7})
\end{lstlisting}
Since this output has interleaved stages, so theres no way a syntactically seperated term could directly reduce to it.

We resolve this mismatch by introducing one more translation, called {\em masking} and written $[\xi;v] \vsplito \mathcal{V}$,
which converts residual tables and partial values like the those above into a syntactically seperated version $\mathcal{V}$.
As before, we enforce the ``syntactically seperated'' property structurally,
saying that $\mathcal{V}$ must have the form $\mval i q$ (called a {\em masked value}) where 
$i$ is a monostage value respresenting the stage \bbone\ part of $v$,
and $q$ is a monostage term representing all of the stage \bbtwo\ computation in $\xi$ and $v$.

@@

Masking assigns purely stage~\bbone\ values to the immediate value
and likewise assign references into the residual table to the resumer.
In both cases, the offside component is assigned to \texttt{()}, to represent trivial information.

>>>>

Similar to above, we also define a $\sepredtwosym$ relation which can be used to evaluate \texttt{sepM} terms,
with one complication arising from the fact that \lang\ terms at world \bbonem\ produces multistage output.
For example, consider the term
\begin{lstlisting}
(next {1+2}, pure{3+4})
\end{lstlisting}
which reduces (via $\redonesym$) to the residual table and partial value
\begin{lstlisting}
[yhat |-> 1+2] (next {yhat}, pure{7})
\end{lstlisting}
Since this output has interleaved stages, theres no way a syntactically seperated term could directly reduce to it.

We resolve this mismatch by introducing one more translation, called {\em masking} and written $[\xi;v] \vsplito \mathcal{V}$,
which converts residual tables and partial values like the those above into a syntactically seperated version $\mathcal{V}$.
As before, we enforce the ``syntactically seperated'' property structurally,
saying that $\mathcal{V}$ must have the form $\mval i q$ (called a {\em masked value}) where 
$i$ is a monostage value respresenting the stage \bbone\ part of $v$,
and $q$ is a monostage term representing all of the stage \bbtwo\ computation in $\xi$ and $v$.
Note that masking exists only for the purposes of stating correctness; it is not part of the splitting algorithm itself.

@@

Masking assigns purely stage~\bbone\ values to the immediate value
and likewise assigns references into the residual table to the resumer.
In both cases, the alternate component is assigned to $\tup{}$, to represent trivial information.
